GPU-friendly Stroke Expansion

### 2024-04-26 paper.tex
Add figures for error metric
This adds figures for the cubic to Euler spiral error metric, as well as code and gnuplot scripts to draw them. It's a bit minimal still, but does at least add a visual to support the math and the claim.

Possible image for this: the heatmap from the cleaner parallel curves blog post.

@@

>>>>

@@

A visualization of combined error metric is shown in Figure~\ref{fig:cubic_err}, comparing measured and approximate error for a slice of the parameter space, fixing the endpoint angles to 0.1 and 0.2, and varying the distance from both endpoints to the control point.

\begin{figure}
    \includegraphics[scale=0.75]{cubic_err_measured} \includegraphics[scale=0.75]{cubic_err_approx}
    \caption{Comparision of measured (top) and approximated (bottom) error for cubic Bézier to Euler spiral conversion. Scale is log (base 10) of the error.}
    \Description{TODO}
    \label{fig:cubic_err}
\end{figure}
